The problem and promise of scale in animal social multilayer networks

### 2020-02-10 paper/manuscript.Rmd
so many more refs

Sociality exists across both temporal and spatial scales (Whitehead 2008). For
example, grooming requires close spatial proximity between conspecifics and
occurs over brief time periods (e.g. Carter et al. 2015), whereas social
association represents shared space use by members of the same social group
(Figure \@ref(fig:spacetime), Franks et al. 2010). Further, for social
interactions or associations to occur individuals must share space, and thus
have overlapping home ranges. In the context of the social environment, home
range overlap is a relatively coarse scale of sociality across which individuals
share space over coarser spatial and temporal scales (e.g. Piza-Roca et al.
2018). Although the social environment clearly scales spatially and temporally,
it remains unclear whether coarser scales of sociality, including social
association and home range overlap, vary predictably with social interaction
 [@Castles_2014; @Farine2015a]. Thus, we define social scale as the type of
social relationship observed that can be explicitly defined and measured [@Farine_2015a].

Animal social network analysis is a well-developed tool used to measure the
relationships of individuals and organization of social systems (Krause et al.
2009; Wey et al. 2008; Croft et al. 2008). Social network analysis provides
insight into the structure of social communities and social network properties,
which can influence population dynamics and evolutionary processes
(Pinter-Wollman et al. 2014; Kurvers et al. 2014). Despite the widespread use
and innovation of traditional social network analysis (Webber & Vander Wal
2019), it typically considers a single scale of sociality in a given network
(monolayer), drastically simplifying the potential complexity of animal social
systems [@Finn_2019].

Unlike traditional monolayer social networks, multilayer networks explicitly
consider social systems across contexts, including scale-dependent contexts
(Pilosof et al. 2017). Multilayer networks are made up of multiple layers, each
representing (i) different classes of individuals, e.g. male or female; (ii) types 
of behaviours, e.g. grooming, travelling, or foraging; and (iii) spatial areas,
e.g. local or regional, or temporal windows, e.g. daily or seasonal 
(Kivela et al. 2014; Porter 2018). Multilayer networks are relatively novel to studies of animal
behaviour [Silk_2018; @Finn_2019], although they have been used to
describe multidimensional human social systems, complex transportation networks,
and neural networks [@Silk_2018]. The role of scale within multilayer
social networks remains unexplored but provides a unique opportunity to develop
novel understanding of variation in the temporal or spatial scales associated
with social systems.

@@

Studies of social network analysis vary in the number and frequency of
observations as well as the data collection technique used to generate networks
(Davis et al. 2018; Webber and Vander Wal 2019). In addition to altering the
temporal scale by adjusting the time window, we investigated the influence of
the number of observations on resulting multilayer networks. We randomly
selected 500 timesteps and iteratively included 25 additional observations,
regenerating the multilayer network and calculating associations of individuals.
Subsequent iterations included the previous set of observations to mimic
observational data. <!-- TODO: bah conclude / this sentence falls off a cliff -->

>>>>

Sociality exists across both temporal and spatial scales (Whitehead 2008). For
example, grooming requires close spatial proximity between conspecifics and
occurs over brief time periods [e.g. @Carter_2015], whereas social
association represents shared space use by members of the same social group
[Figure \@ref(fig:spacetime), @Franks_2010]. Further, for social
interactions or associations to occur individuals must share space, and thus
have overlapping home ranges. In the context of the social environment, home
range overlap is a relatively coarse scale of sociality across which individuals
share space over coarser spatial and temporal scales [e.g. @Piza_Roca_2018]. 
Although the social environment clearly scales spatially and temporally,
it remains unclear whether coarser scales of sociality, including social
association and home range overlap, vary predictably with social interaction
 [@Castles_2014; @Farine2015a]. Thus, we define social scale as the type of
social relationship observed that can be explicitly defined and measured [@Farine_2015a].

Animal social network analysis is a well-developed tool used to measure the
relationships of individuals and organization of social systems 
[@Krause_2009; @Wey_2008; @Croft_2011]. Social network analysis provides
insight into the structure of social communities and social network properties,
which can influence population dynamics and evolutionary processes
[@Pinter_Wollman_2013; @Kurvers_2014]. Despite the widespread use
and innovation of traditional social network analysis [@Webber_2019], 
it typically considers a single scale of sociality in a given network
(monolayer), drastically simplifying the potential complexity of animal social
systems [@Finn_2019].

Unlike traditional monolayer social networks, multilayer networks explicitly
consider social systems across contexts, including scale-dependent contexts
[@Pilosof_2017]. Multilayer networks are made up of multiple layers, each
representing (i) different classes of individuals, e.g. male or female; (ii) types 
of behaviours, e.g. grooming, travelling, or foraging; and (iii) spatial areas,
e.g. local or regional, or temporal windows, e.g. daily or seasonal 
 [@Kivela_2014; @Porter_2018]. Multilayer networks are relatively novel to studies of animal
behaviour [Silk_2018; @Finn_2019], although they have been used to
describe multidimensional human social systems, complex transportation networks,
and neural networks [@Silk_2018]. The role of scale within multilayer
social networks remains unexplored but provides a unique opportunity to develop
novel understanding of variation in the temporal or spatial scales associated
with social systems.

@@

Studies of social network analysis vary in the number and frequency of
observations as well as the data collection technique used to generate networks
[@Davis_2018; @Webber_2019]. In addition to altering the
temporal scale by adjusting the time window, we investigated the influence of
the number of observations on resulting multilayer networks. We randomly
selected 500 timesteps and iteratively included 25 additional observations,
regenerating the multilayer network and calculating associations of individuals.
Subsequent iterations included the previous set of observations to mimic
observational data. <!-- TODO: bah conclude / this sentence falls off a cliff -->
